Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-23 AO_bondedSi.tex
add circle A

In the limit $\lim_{d \to 0} T_e \rightarrow T_{DSP}} $ and the etalon approaches 100\% transmission.  Figure \ref{figAbsoluteTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 0, 20, 35, 60, 350, and 3500 nm.

>>>>

In the limit $\lim_{d \to 0} T_e \rightarrow T_{DSP}} $ and the etalon approaches 100\% transmission.  Figure \ref{figAbsoluteTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 0, 20, 35, 60, 350, and 3500 nm.  The bottom two panels show the ``gap'' transmission, the value of the throughput with the losses from the outer Si cavities divided out.  For the very largest gap, large fringes appear as the cavity resonance of the air gap modulates the transmission.  Below a $\lambda/2$ gap size the effect of the gap manifests itself as a wavelength-dependent diminution of the transmission.  For the smallest $35-60$ nm gaps, there is a $2-6\%$ decrease in gap transmission from 2400 nm down to 1250 nm.  It is the magnitude and wavelength dependence of this transmission spectrum that provides information about the axial extent of the gap.
